\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{comment}
\usepackage{marvosym}
\usepackage{setspace}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{tikz}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\faCenter}[1]{\raisebox{-2pt}{\faIcon{#1}}}

\definecolor{theme_color}{rgb}{0.11, 0.51, 0.30}
\definecolor{grey}{rgb}{0.35, 0.35, 0.35}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\color{theme_color}\raggedright\LARGE
}{}{0em}{\begin{tikzpicture}[remember picture,overlay]
\path[left color=theme_color, right color=white]
(-7pt,-7pt)+(0,-2pt) rectangle +(14cm,2pt);
\end{tikzpicture}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength\parindent{24pt}
\setstretch{1.15}
\begin{document}

\begin{center}
\textbf{\Huge{\scshape{\textcolor{theme_color}{Javad}}}} \textbf{\Huge{\scshape{\textcolor{black}{Sheikh}}}}
\vspace{-20pt}
\end{center}
\begin{tikzpicture}[baseline]
    \path[left color=white,right color=white,middle color=theme_color]
    (-5pt,-5pt)+(0,-2pt) rectangle +(\textwidth,2pt);
\end{tikzpicture}
\begin{center}
\begin{tabularx}{1\textwidth} {>{\raggedleft\arraybackslash}X >{\centering\arraybackslash}X >{\raggedright\arraybackslash}X}
    \faCenter{globe} \href{https://javad-sheikh.github.io}{Personal Website} &
    \faCenter{envelope} \href{mailto:javad2n@aut.ac.ir}{javad2n@aut.ac.ir}  &
    \faCenter{linkedin}  \href{https://linkedin.com/in/javad-sheikh}{linkedin.com/in/javad-sheikh} \\
    \faCenter{phone-alt} \href{tel:+989197317364}{+98-919-7317-364} &
    \faCenter{orcid} \href{https://orcid.org/0000-0001-6474-1674}{0000-0001-6474-1674} &
    \faCenter{github} \href{https://github.com/javad-sheikh}{github.com/javad-sheikh}  \\

\end{tabularx}
\end{center}

\begin{comment}
\begin{center}
    \textbf{\Huge \scshape Javad Sheikh} \\ \vspace{1pt}
    dokhaniat 4, first sayyad, sayyad Blvd.,  Gorgan, Iran 4917973354\\
    \href{https://www.researchgate.net/profile/Javad-Sheikh-2}{researchgate.net/profile/Javad-Sheikh} $|$
    \href{https://github.com/javad-sheikh}{github.com/javad-sheikh}  $|$
    \href{https://linkedin.com/in/javad-sheikh}{linkedin.com/in/javad-sheikh}\\
    \small \href{tel:+989197317364}{+98-919-7317-364} $|$ \href{mailto:javad2n@yahoo.com}{javad2n@yahoo.com}
\end{center}
\end{comment}
%\section{Profile}

%\indent I'm a highly motivated artificial intelligence graduate who enjoys solving problems meticulously. I'm looking to improve my knowledge about Machine Learning, Deep Learning, their applications and deploy them into real-world models.
%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Amirkabir University of Technology}{Tehran, Iran}
        {M.Sc. in Computer Engineering, Minor in Artificial Intelligence and robotics}{Sep. 2018 -- Now}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis:} ``Anomaly detection on time series using deep neural networks.''}
        \resumeItem{\textbf{Advisor:} Prof. Safabakhsh}
        %\resumeItem{\textbf{GPA:} 15.77/20}
      \resumeItemListEnd
    \resumeSubheading
      {Amirkabir University of Technology}{Tehran, Iran}
      {B.Sc. in Biomedical Engineering, Minor in Bioelectrics}{Sep. 2013 -- Sep. 2018}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis:} ``Design and Implementation of mobile room lighting control equipment for patients with paraplegic patients.''}
        \resumeItem{\textbf{Advisor:} Dr. Ahmadi Pajouh}
        %\resumeItem{\textbf{GPA:} 14.78/20}
        \resumeItemListEnd
    \resumeSubheading
      {Shahid Beheshti Highschool}{Gorgan, Iran}
      {Diploma in Mathematics and Physics Discipline}{Sep. 2009 -- Sep. 2013}
      \resumeItemListStart
        \resumeItem{Under the supervision of NODET (National Organization for Developing Exceptional Talents)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{\textbf{Publications}}
    \resumeItemListStart
        \resumeItem{
        \textbf{Book chapter:}\\
        Shariatzadeh F.J., Salar Amoli M., Faghihi F., \textbf{Sheikh J.},Sadeghi P., et al.; 2021; \textit{Sutures and surgical instruments};  Medical Equipment;}

        \resumeItem{
        \textbf{Journal papers:}\\
        Sheikh V., RezaeiMoghaddam H., Jafary R., Gholami Z., \textbf{Sheikh J.}; 2020; \textit{Design, construction and performance evaluation of an automatic weighing lysimeter.}; Water and Irrigation Management; 10(1); pp.61-73.\\
        \textbf{DOI: }\href{https://dx.doi.org/10.22059/jwim.2020.294404.738}{dx.doi.org/10.22059/jwim.2020.294404.738}}

        \resumeItem{
        Nazarimehr F., \textbf{Sheikh J.}, Ahmadi M.M., Pham V.T., Jafari S.; 2018; \textit{Fuzzy predictive controller for chaotic flows based on continuous signals.}; Chaos, Solitons \& Fractals; 106; pp.349-354.\\
        \textbf{DOI: }\href{https://doi.org/10.1016/j.chaos.2017.12.005}{doi.org/10.1016/j.chaos.2017.12.005}}

    \resumeItemListEnd
\section{\textbf{Selected Academic Projects}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Tracking moving object in video} $|$ \emph{Python, OpenCV}}{}
          \resumeItemListStart
            \resumeItem{Extracting key points using Brief, Freak, Surf, and Sift}
            \resumeItem{Following key points utilizing RANSAC and Least Median}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Generative Adversarial Network} $|$ \emph{Python, Tensorflow, Google Colab, Gradient Tape}}{}
          \resumeItemListStart
            \resumeItem{Generation cat and dog pictures with GAN network using the cats and dogs data set}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Semantic Segmentation} $|$ \emph{Python, Tensorflow, Google Colab, CNN}}{}
          \resumeItemListStart
            \resumeItem{Semantic segmentation of KITTI data set using convolutional neural networks}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Machine Translation} $|$ \emph{Python, Tensorflow, LSTM, GRU, Attention}}{}
          \resumeItemListStart
            \resumeItem{Designed an Encoder-Decoder Recurrent Neural Network model with attention for Deutsch to English translation}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Fuzzy Neural Network} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Estimation of Mackey-Glass time series with a fuzzy neural network}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Machine learning Projects} $|$ \emph{Python, scikit-learn}}{}
          \resumeItemListStart
            \resumeItem{Clustering tasks using  Kmeans, DB-Scan and Hierarchical clustering }
            \resumeItem{Classification with KNN with k found using K—fold-cross-validation}
            \resumeItem{Classification with  C4.5, CART, ID3 Decision Trees}
            \resumeItem{Classification with Random Forest}
            \resumeItem{Classification of car evaluation data set with Naive Bayes and Logistic Regression}
            \resumeItem{Classification of handwritten digits data set with SVM}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Parameter Estimation} $|$ \emph{Matlab, Optimization}}{}
        \resumeItemListStart
            \resumeItem{Parameter Estimation of the Rulkov Neuron Map using Interior search algorithm)}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
\section{\textbf{Working Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {freelance AI engineer}{Apr. 2019 -- Present}
      {Retinopathy detection App Development}{}
      \resumeItemListStart
        \resumeItem{Preprocessed retina images from Kaggle Diabetic Retinopathy data set}
        \resumeItem{retrained DenseNet-169 on a data set previously preprocessed}
        \resumeItem{Developed AI mobile application to detect diabetic retinopathy}
      \resumeItemListEnd
    \resumeSubSubheading
     {Time series forecasting}{}
     \resumeItemListStart
        \resumeItem{Deployed different forecasting methods like Arima, Sarima, and recurrent neural networks  }
     \resumeItemListEnd
    \resumeSubheading
      {Artificial Intelligence App Developer}{Sep. 2018 -- Mar. 2019}
      {AI engineer at Sibbank}{Tehran}
      \resumeItemListStart
        \resumeItem{Researched and assessed different mobile compatible deep learning structures}
        \resumeItem{Used transfer learning to retrain Mobilenet-192}
        \resumeItem{Developed AI mobile application to read credit card number and expiration from images taken with mobile camera}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{\textbf{Teaching Experience}}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Software Tutor} $|$ \emph{Python, Tensorflow, Google Colab}}{Spring 2019}
          \resumeItemListStart
            \resumeItem{Department of Computer Engineering, Amirkabir University of Technology}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Software Tutor} $|$ \emph{MATLAB, Simulink}}{Spring 2015}
          \resumeItemListStart
            \resumeItem{Department of Biomedical Engineering, Amirkabir University of Technology}
          \resumeItemListEnd
      \resumeItemListEnd

\section{\textbf{Languages}}
  \resumeSubHeadingListStart
    \resumeSubSubheading
        {\textbf{English} (IELTS Academic CEFR level: C1)}{Listening: 8.5, Reading: 8.5, Writing: 6.5, Speaking: 7}

    \resumeSubSubheading
        {\textbf{German} (Elementary)}{}

  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{\textbf{Programming Languages:}{Python, Java, Matlab, C/C\texttt{++}, SQL, JavaScript, HTML/CSS}}
     
     \item{\textbf{Developer Tools:}{ Visual Studio Code, Android Studio, Google Colab, Kaggle}}
     
     \item{\textbf{Version Control:}{Git, GitHub, GitLab}}
     
     \item{\textbf{Selected Python Libraries:}{ Tensorflow, Pytorch, OpenCV, Pandas, NumPy, Matplotlib, Scipy, Scikit-Learn}}
     
     \item{\textbf{Typesetting:}{\TeX, Word}}
     
     \item{\textbf{Operating Systems:}{Windows, Ubuntu}}
    }
 \end{itemize}
 
\section{\textbf{Honors \& Awards}}

  \resumeSubHeadingListStart  
    \resumeSubSubheading
        {\textbf{M.Sc. National University Entrance Exam}}{}
        \resumeItemListStart
            \resumeItem{Achieved the 87th place in the national M.Sc entrance exam in Computer Engineering}
          \resumeItemListEnd
    \resumeSubSubheading
        {\textbf{B.Sc. National University Entrance Exam}}{}
        \resumeItemListStart
            \resumeItem{Ranked in the top 0.5\% among 251,000 students in the national university entrance exam in mathematics and physics discipline}
          \resumeItemListEnd
    \resumeSubSubheading
        {\textbf{B.Sc. National University Entrance Exam}}{}
        \resumeItemListStart
            \resumeItem{Ranked in the top 5\% among 10,000 students in the national university entrance exam in foreign languages discipline}
          \resumeItemListEnd
    \resumeSubSubheading
        {\textbf{High School Olympiad}}{}
        \resumeItemListStart
            \resumeItem{being accepted at the first stage of national Chemistry Olympiad (2011)}
          \resumeItemListEnd
    
  \resumeSubHeadingListEnd
  
\section{\textbf{Research Interests}}
    \resumeItemListStart
            \resumeItem{Machine Learning}
            \resumeItem{Artificial Neural Networks}
            \resumeItem{Biologically Plausible Neural Networks}
            \resumeItem{Anomaly Detection}
            \resumeItem{Computer Vision}
            \resumeItem{Medical Image Analysis}
          \resumeItemListEnd
          
\section{\textbf{References}}
    \resumeSubHeadingListStart

        \resumeSubSubheading
            {\textbf{Prof. Safabakhsh,} Department of Computer Engineering, Amirkabir University of Technology}{}

            {\textbf{Email: }}{\href{mailto:safa@aut.ac.ir}{safa@aut.ac.ir}}

        \resumeSubSubheading
            {\textbf{Asst. Prof. Nazerfard,} Department of Computer Engineering, Amirkabir University of Technology}{}

            {\textbf{Email: }}{\href{mailto:nazerfard@aut.ac.ir}{nazerfard@aut.ac.ir}}

        \resumeSubSubheading
            {\textbf{Assoc. Prof. Jafari,} Department of Biomedical Engineering, Amirkabir University of Technology}{}

            {\textbf{Email: }}{\href{mailto:sajadjafari@aut.ac.ir}{sajadjafari@aut.ac.ir}}
    \resumeSubHeadingListEnd
\end{document} 